On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-03-28 docs/mvfits_paper/mvf.tex
Fix reference for QNM j_f +/- branches [9]

In particular, it is shown that the two branches (namely $\jf>0$ and $\jf<0$) naturally form a single family of solutions when accounting for the sign of the \bh{}'s oriented spin \cite{Husa:2007hp}.

>>>>

In particular, it is shown that the two branches (namely $\jf>0$ and $\jf<0$) naturally form a single family of solutions when accounting for the sign of the \bh{}'s oriented spin \cite{Husa:2015iqa}.
